Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations -- Outline

### 2017-04-25 Ben_Manuscripts/Outlines/Paper1_Outline.tex
updates

>>>>

	Questions to answer from here:
	\begin{itemize}
		\item What is the relative stability of the disordered vs ordered state? (Free energy calculation)
		\item Which phase is prevalent across a range of temperatures? Can replica exchange tell us what where the system prefers to spend its time?
		\item Do we observe both phases experimentally? (would be nice but probably not feasible for our timeline without some luck)
	\end{itemize}
